%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.982\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Mayank Aggarwal} \\ \vspace{1pt}
    % 123 Street Name, Town, State 12345 \\ 
    \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-8860729957 ~ \href{mailto:mayankagg9722@gmail.com}{\faEnvelope\  mayankagg9722@gmail.com} ~ 
    \href{https://in.linkedin.com/in/mayankagg9722}{\faLinkedin \ in/mayankagg9722}  ~
    \href{https://github.com/mayankagg9722}{\faGithub\ mayankagg9722} ~
    \href{http://mayankagg9722.github.io/}{\faGlobe\ Portfolio}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
   \section{EDUCATION}
  \resumeSubHeadingListStart
    % \small{
    \resumeSubheading
      {Vellore Institute of Technology, Vellore}{May 2015 -- May 2019}
      {Bachelor of Technology in Computer Science}{CGPA: 8.50}
    \resumeSubheading
      {Vivekanand School, Delhi}{March 2015 \& March 2013}
      {Class: XII(CBSE) \& Class: X(CBSE)}{Score: 91.50\% \& CGPA: 10}
      % }
  \resumeSubHeadingListEnd
  
% %-----------EXPERIENCE-----------
 \section{EXPERIENCE}
   \resumeSubHeadingListStart
    % \small{
    \resumeSubheading
       {Microsoft, Azure}{Sept. 2025 - Present}
       {\textbf{Senior Software Development Engineer}}{Hyderabad, India}
       \resumeItemListStart
         \resumeItem{Currently building resiliency capabilities with backup and disaster recovery for \href{https://learn.microsoft.com/en-us/azure/cosmos-db/introduction}{\bf \underline{Azure Cosmos DB}}, ensuring enterprise-grade data protection and business continuity for mission-critical workloads.}
         \resumeItem{Led \href{https://learn.microsoft.com/en-us/azure/backup/backup-overview}{\underline{Azure BCDR}} engineering team for AKS in designing and delivering enterprise grade GA (General Available) Data Protection solution for \href{https://learn.microsoft.com/en-us/azure/backup/azure-kubernetes-service-backup-overview}{\bf \underline{Azure Kubernetes Service}} ensuring robust backup and disaster recovery capabilities for critical workloads. Actively contribute to \href{https://github.com/vmware-tanzu/velero}{\bf \underline{Velero}} open source project (CNCF) for Kubernetes backup and disaster recovery.}
         \resumeItem{Onboarded Fortune 500 enterprise customers and supported more than a \textbf{million} backups with SLA of \textbf{99.99} for backup and restore with SLA of \textbf{100}. Presented the Azure AKS BCDR solution in \textbf{KubeCon Europe Paris} 2024 engaging with over \textbf{15000} attendees which was hosted by \textbf{Linux Foundation}.}
       \resumeItemListEnd

     \resumeSubheading
       {Microsoft, Azure}{June 2019 -- Sept. 2025}
       {Software Development Engineer 1 \& 2}{Hyderabad, India}
       \resumeItemListStart
         \resumeItem{Built out the abstraction in the control plane, delivering the highly distributed and scalable \href{https://docs.microsoft.com/en-us/azure/service-fabric/service-fabric-overview}{\bf \underline {Service Fabric}} microservice from the ground up. Led the development of the core \textbf{Workflow State Machine}, enabling seamless integration of workload plugins such as Azure Disk and AKS for long-running backup and restore workflows.}
         \resumeItem{Led and mentored interns on the integration of \href{https://azure.microsoft.com/en-in/services/cache/}{\bf \underline{Distributed Redis cache}} in the management plane to optimize performance, resulting in significant latency reduction by 30\%.}
         \resumeItem{Implemented and delivered the foundational  \href{https://learn.microsoft.com/en-us/azure/backup/create-manage-backup-vault\#move-a-backup-vault-across-azure-subscriptionsresource-groups}{\bf \underline{Resource Move}} capability for Azure BCDR, enabling customers to efficiently migrate Azure resources at scale across subscriptions and tenants during large-scale migrations.}
         \resumeItem{Developed a manifest-driven, dynamic user interface feature for the Azure BCDR Portal using TypeScript, enabling scalable UI architecture and seamless onboarding of multiple workloads without requiring code changes.}
         \resumeItem{Worked for onboarding \href{https://docs.microsoft.com/en-us/azure/backup/backup-vault-overview}{\bf \underline{backup vault service}} to secure government Azure cloud for China and United States.}
       \resumeItemListEnd

    % \resumeSubheading
    %    {Microsoft}{May to July 2018 -- Jan to June, 2019}
    %    {Software Engineer Intern}{Hyderabad, India}
    %    \resumeItemListStart
    %      \resumeItem{Designed and implemented migration from V1 to V2 user interfaces for the \href{https://azure.microsoft.com/en-in/products/devops/?msockid=215053d7170b6d8f2545474d16f96cfb}{\bf \underline{Azure DevOps}} self-service extension, ensuring compliance to meet accessibility standards for Azure interfaces. It includes \href{https://developer.mozilla.org/en-US/docs/Web/Accessibility}{\bf \underline A11Y, WCAG 2.1} and tools like Narrator, JAWS, and NVDA so that \textbf{specially-abled} person can access user interfaces. Also enhanced UX by developing the search and auto-complete functionality which enabled direct navigation to any level in the services tree hierarchy.}
    %      \resumeItem{Able to secure full time job offer post internship in 2018 (3rd year) during college with this internship among more than 100 intern candidates from across India.}
    %    \resumeItemListEnd

    % \resumeSubheading
    %    {Dipper Technologies Pvt. Ltd.}{Dec 2017 – Jan 2018}
    %    {Android Developer Intern}{New Delhi, India}
    %    \resumeItemListStart
    %     \resumeItem{Responsible for designing core intelligent delivery progressive web application using \textbf{Angular 2} for \href{https://www.youtube.com/watch?v=D-unLCisymE}{\bf \underline{truckers}} and \href{https://www.youtube.com/watch?v=W6yJtqacrLA}{\bf \underline{shippers}} Android or iOS mobile users.}
    %    \resumeItemListEnd
    % }
   \resumeSubHeadingListEnd
 \vspace{-16pt}


%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    % \textbf{Areas of Interest}{: Competitive Programming, Web Development, Blockchain } \\
     \textbf{Languages}{: C++, C\#, Golang, .NET, Java, Python, Flask, NodeJS, Bash} \\
     \textbf{Cloud, Infrastructure}{: Azure, Kubernetes, Docker, AWS} \\
      \textbf{Databases}{: SQL, MongoDB, Azure Table, Blob, Fileshares, Firebase} \\
     \textbf{Mobile and Web}{: Android, ReactJS, ExpressJS, AngularJS, HTML5/CSS3, Typescript, JavaScript, JQuery, Bootstrap} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    % \small{
    \resumeProjectHeading
          {\textbf{Gardianscale | Next-Gen CI/CD Platform}}{\href{https://gardianscale.com}{\bf \underline{Project Link}}}
          \resumeItemListStart
            \resumeItem{Built a next-generation CI/CD platform with intelligent elastic caching (Node, Docker, Java, Python) and automatic infrastructure provisioning using {\bf Kubernetes, Docker, and Go}, accelerating builds by up to \textbf{50x} with zero configuration and providing \textbf{4x} faster cache performance through intelligent caching mechanisms.}
          \resumeItemListEnd
          \vspace{-19pt}
    \resumeProjectHeading
          {\textbf{VIT GO | Android Application }}{ {\href{https://github.com/mayankagg9722/VIT-Go}{\underline {\normalsize Project Link}}}}
          \resumeItemListStart
            \resumeItem{Developed high traffic Android App  with over \textbf{33K} users with over \textbf{100K impressions} per day which aims to bring every academic details on their fingertips. It displays all the academic information for students and with a lot of customize features. This app also \textbf{ranked 3\textsuperscript{rd}} in productivity category in India on Google Play Store.}
          \resumeItemListEnd
          \vspace{-19pt}
      \resumeProjectHeading
          {\textbf{EDGE.FIT | AI Gym Trainer}}{\href{https://github.com/mayankagg9722/MSFTGaradge-IOTEdge-SmartGym}{\bf \underline{Project Link}}}
          \resumeItemListStart
            \resumeItem{It is a virtual personal fitness trainer which uses {\bf Computer vision}, and Intelligent Edge and Cloud computing to help users achieve their fitness goals efficiently.}
          \resumeItemListEnd
          \vspace{7pt}
          % }
    \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Microsoft Garage Hackathon: }\emph{1\textsuperscript{st}/85 teams. }{\href{https://youtu.be/0-dl__J98mo}{\underline {Link}}} \\
     \textbf{NASA SpaceAppChallange'17: }\emph{18\textsuperscript{th}/105 globally in world. }{\href{https://2017.spaceappschallenge.org/challenges/planetary-blues/wheres-water/teams/team-go}{\underline {Link}}} \\
     \textbf{Apple Developers Group, App-A-Thon'17: }\emph{2\textsuperscript{nd}/100 teams. } {\href{https://www.youtube.com/watch?v=jBxkavGlVPU}{\underline {Link}}} \\
     \textbf{Google Developers Hackathon - Devfest'16: }\emph{Platinum Prize Winners. } {\href{https://github.com/mayankagg9722/miBeatChat}{\underline {Link}}} \\
    }}
 \end{itemize}
 \vspace{-16pt}

 %-----------ACHIEVEMENTS-----------
\section{SOCIETIES}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \href{https://gdg.community.dev/gdg-on-campus-vellore-institute-of-technology-chennai-india/}{\textbf{Google Developer Group}}, \href{https://www.teamsammard.com/}{\textbf{Team Sammard}}, \href{https://in.linkedin.com/company/creationlabs}{\textbf{Creation Labs}}, \href{https://ieeecsvit.com/}{\textbf{IEEE-CS}} {}\\
    }}
 \end{itemize}
 \vspace{-16pt}

 \end{document}
